Proof of Identity

### 2022-06-26 paper.tex
registerKid notation

\newpage
\section{Registering $\khk$ (Person key)}
\begin{enumerate}
  \item Register $\kid$ on \pbc, by calling 
    $$register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK).$$

@@

  \item Register $\khk$ on \pbc, by calling 
    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
  where:
    \begin{enumerate}
      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
    \end{enumerate}
\end{enumerate}

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
//Key is eID private key, or PrivateeIDKey("")
//PersonKey is Blockchain key used by a Person
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public PinKUsed;
  mapping(uint256 => uint256) public PinKPUsed;
  mapping(uint256 => uint256) public PinKPLastConfirmed;
  mapping(uint256 => bool) public PInvalid;
  mapping(uint256 => bool) public KInvalid;
  //TODO:CA fields!

  //K_1=K_1("registerK")
  //Pin=H(Pin)
  function registerK public(
    uint256 Pin,
    uint256 K_1,
    bytes proofPinOwnsK
  ){
    uint256 previousKey = PinKUsed[Pin];
    if(previouseKey == K_1)
      return;
    bool isOwner = zksnarkverify(VK, [
        PIN, 
        K_1
      ],
      proofPINOwnsK);
    if(isOwner && ! KInvalid[K_1]){
      if(previousKey!=0)
        KInvalid[previousKey]=true;
      PinKUsed[Pin]=K_1;
    }
  }

>>>>

\newpage
\section{Registering $\khk$}
\begin{enumerate}
  \item Register $\kid$ on \pbc, by calling 
    $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsK).$$

@@

    The reasoning behind the choice of arguments for the $register\kid$ function:

    If we used:
    \begin{itemize}
      \item $register\kid(H(Nin, \kid^{-1}("register\kid")), proofNinOwnsK)$

        TODO: explain
      \item $register\kid(Nin, \kid^{-1}("register\kid"), proofNinOwnsK)$

        TODO: explain
    \end{itemize}

  \item Register $\khk$ on \pbc, by calling 
    $$register\khk(Nin\kid, Nin\kid\khk, proof)$$
  where:
    \begin{enumerate}
      \item $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$
    \end{enumerate}

  The Person registers a $\khk$, which is a unique public key tied to the Person on the \pbc{}.
  What is the meaning behind $register\khk$ function?
  \begin{itemize}
    \item Sybil resistance. $\khk$ is the only such key that is tied to the Person with the samo $Nin$.
      By design, the Person can not own two valid $\khk$s at the same time.

      TODO: Explanation/proof.
    \item Anonimity. Someone with a database of all the $\kid$ public keys or/and the database of all the $\khk$ public keys, shouldn't be able to determine which $Nin$, $\kid$ or $\khk$ was used, from the function call.

    TODO: Explanation/proof.

    The assumption is that the CA doesn't have access to $\kid^{-1}$, i.e. that $\kid$ is generated safely on the eID.
  \end{itemize}
  The reasoning behind the choice of arguments for the $register\khk$ function:

  TODO: 
\end{enumerate}

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
//Key is eID private key, or PrivateeIDKey("")
//PersonKey is Blockchain key used by a Person
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public NinKidUsed;
  mapping(uint256 => uint256) public NinKidKpUsed;
  mapping(uint256 => uint256) public NinKidKpLastConfirmed;
  mapping(uint256 => bool) public KpInvalid;
  mapping(uint256 => bool) public KidInvalid;
  //TODO:CA fields!

  //vKid=KidPrivate("registerKid")
  //Nin=H(Nin)
  function registerKid public(
    uint256 Nin,
    uint256 vKid,
    bytes proofNinOwnsKid
  ){
    uint256 previousKey = NinKidUsed[Nin];
    if(previousKey == vKid)
      return;
    bool isOwner = zksnarkverify(VK, [
        Nin, 
        vKid
      ],
      proofPINOwnsKid);
    if(isOwner && ! KidInvalid[vKid]){
      if(previousKey!=0)
        KidInvalid[previousKey]=true;
      NinKidUsed[Nin]=vKid;
    }
  }
